%
% File checkpoint2.tex
%

\documentclass[11pt,letterpaper]{article}
\usepackage{naaclhlt2016}
\usepackage{times}
\usepackage{latexsym}

\naaclfinalcopy % Uncomment this line for the final submission
\def\naaclpaperid{***} %  Enter the naacl Paper ID here

% To expand the titlebox for more authors, uncomment
% below and set accordingly.
% \addtolength\titlebox{.5in}    

\newcommand\BibTeX{B{\sc ib}\TeX}


\title{Emotion Identification within Text Messages}

% Author information can be set in various styles:
% For several authors from the same institution:
% \author{Author 1 \and ... \and Author n \\
%         Address line \\ ... \\ Address line}
% if the names do not fit well on one line use
%         Author 1 \\ {\bf Author 2} \\ ... \\ {\bf Author n} \\
% For authors from different institutions:
% \author{Author 1 \\ Address line \\  ... \\ Address line
%         \And  ... \And
%         Author n \\ Address line \\ ... \\ Address line}
% To start a seperate ``row'' of authors use \AND, as in
% \author{Author 1 \\ Address line \\  ... \\ Address line
%         \AND
%         Author 2 \\ Address line \\ ... \\ Address line \And
%         Author 3 \\ Address line \\ ... \\ Address line}
% If the title and author information does not fit in the area allocated,
% place \setlength\titlebox{<new height>} right after
% at the top, where <new height> can be something larger than 2.25in
\author{Quincy Davenport \\ {\bf Michael Dobrowolski} \\ {\bf Jeremy Drouillard}
\\ {\bf Matthew Terwilliger} \\}

\date{}

\begin{document}

\maketitle

\section{Project Description}

Our project is to identify emotions within text. Text messages are personal
modes of communication with valuable aspects such as emojis, exaggerated
punctuation (`!?!?', `…', etc.), highly colloquial texting language (`lol',
`smh', etc.), and relationship indicative contact names. Also, more often than
not, they are also full conversations between at least two people rather than
publicized monologues and single statements.

We plan to have a list of 6 possible emotions to use as labels:
\begin{enumerate}
    \item{Happy}
    \item{Content}
    \item{Indifferent}
    \item{Confused}
    \item{Sad}
    \item{Angry}
\end{enumerate}

Happiness being positive emotion for some specific reason and contentment being
positive emotion in general. Indifference is the unstressed absence of emotion.
Confusion is the stressed absence of emotion, which indicates that it might be
complemented by another emotion.  Sadness and anger are for negative emotion.
Sadness is negative emotion not directed at any object, while anger is negative
emotion with a direct object.

Our project would fall into the category of sentiment analysis. The project
would further differentiate positive and negative emotion for if there is or
isn’t an object of the emotion and it would further differentiate neutral
emotions by polarity. Text messages seem to have more emotional cues, so it
makes sense to push the boundaries of sentiment analysis a little. 

\pagebreak

\section{Related Work}

Manuscripts must be in two-column format.  Exceptions to the
two-column format include the title, as well as the 
authors' names and complete
addresses (only in the final version, not in the version submitted for review), 
which must be centered at the top of the first page (see
the guidelines in Subsection~\ref{ssec:first}), and any full-width
figures or tables.  Type single-spaced.  Do not number the pages 
in the camera-ready version.
Start all pages directly under the top margin.  See the guidelines
later regarding formatting the first page.

The maximum length of a manuscript is eight (8) pages for the main
conference, printed single-sided, plus two (2) pages for references
(see Section~\ref{sec:length} for additional information on the
maximum number of pages). 

By uncommenting {\small\verb|\naaclfinalcopy|} at the top of this 
 document, it will compile to produce an example of the camera-ready formatting; by leaving it commented out, the document will be anonymized for initial submission.  When you first create your submission on softconf, please fill in your submitted paper ID where {\small\verb|***|} appears in the {\small\verb|\def\naaclpaperid{***}|} definition at the top.

The review process is double-blind, so do not include any author information (names, addresses) when submitting a paper for review.  
However, you should maintain space for names and addresses so that they will fit in the final (accepted) version.  The NAACL HLT 2016 \LaTeX\ style will create a titlebox space of 2.5in for you when {\small\verb|\naaclfinalcopy|} is commented out.  

\section{Data Collection}

As the reviewing will be blind, the paper must not include the
authors' names and affiliations.  Furthermore, self-references that
reveal the author's identity, e.g., ``We previously showed (Smith,
1991) ...'' must be avoided. Instead, use citations such as ``Smith
previously showed (Smith, 1991) ...'' Papers that do not conform to
these requirements will be rejected without review. In addition,
please do not post your submissions on the web until after the
review process is complete (in special cases this is permitted: see 
the multiple submission policy below).

We will reject without review any papers that do not follow the
official style guidelines, anonymity conditions and page limits.

\pagebreak
\section{Method Description}
Papers that have been or will be submitted to other meetings or
publications must indicate this at submission time. Authors of
papers accepted for presentation at NAACL HLT 2016 must notify the
program chairs by the camera-ready deadline as to whether the paper
will be presented. All accepted papers must be presented at the
conference to appear in the proceedings. We will not accept for
publication or presentation papers that overlap significantly in
content or results with papers that will be (or have been) published
elsewhere.

Preprint servers such as arXiv.org and ACL-related workshops that
do not have published proceedings in the ACL Anthology are not
considered archival for purposes of submission. Authors must state
in the online submission form the name of the workshop or preprint
server and title of the non-archival version.  The submitted version
should be suitably anonymized and not contain references to the
prior non-archival version. Reviewers will be told: ``The author(s)
have notified us that there exists a non-archival previous version
of this paper with significantly overlapping text. We have approved
submission under these circumstances, but to preserve the spirit
of blind review, the current submission does not reference the
non-archival version.'' Reviewers are free to do what they like with
this information.

Authors submitting more than one paper to NAACL HLT must ensure
that submissions do not overlap significantly ($>25\%$) with each other
in content or results. Authors should not submit short and long
versions of papers with substantial overlap in their original
contributions.

\section*{Acknowledgments}

Do not number the acknowledgment section.

\bibliography{checkpoint2}
\bibliographystyle{naaclhlt2016}


\end{document}
